Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-07-13 tensor/draft/draft-tensor-op.tex
[draft] add appendix on MC methods

Here we describe the theoretical treatment of observables and collect
numerical input of the most relevant parameters. The software package
{\tt EOS} \cite{Bobeth:2011gi, Bobeth:2011nj, EOS} is used for
predictions of observables in $B_s\to \bar\mu\mu$ and $B\to
K^{(*)}\bar\ell\ell$. The fit is performed with the package {\tt
  pypmc}, which incorporates the algorithm presented in
\cite{Beaujean:2013:PMC, Beaujean:2012uj} and in addition an
implementation of the variational Bayes algorithm. \fred{Add, get DOI
  for pypmc version}

@@

\todo{Describe how we do prior/posterior predictive}
%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
%\section{
%  Standard model predictions
%  \label{app:SM:predictions}
%}

>>>>

Here we describe the theoretical treatment of observables and collect numerical
input of the most relevant parameters. The software package {\tt EOS}
\cite{Bobeth:2011gi, Bobeth:2011nj, EOS} is used for the calculation of
observables in $B_s\to \bar\mu\mu$ and $B\to K^{(*)}\bar\ell\ell$ and associated
constraints. Both the likelihood and the prior are defined entirely within EOS.

@@

\section{Monte Carlo sampling}
\label{app:mc}
\todo{reference in main text}
The marginalization of the posterior is performed with the package {\tt
  pypmc}~\cite{beaujean_2015_20045}, which incorporates the algorithm presented
in \cite{Beaujean:2013:PMC, Beaujean:2012uj} and in addition an implementation
of the variational Bayes algorithm. In every analysis we first run multiple
adaptive Markov chains (MCMC) in parallel through \texttt{pypmc}. If necessary,
chains are seeded at the SM point to exclude solutions in which multiple
nuisance parameters simultaneously deviate strongly from prior expectations.

In total, there are 19 parameters $\alpha^i_j$ to describe $B\to K^*$ form
factors and most of them are strongly correlated. But it is well known that
strong correlation leads to poor sampling as it can cause the random-walk Markov
chains to spend significant time in regions of low probability and thus produce
spurious peaks. To mitigate this issue, we perform a fit to form-factor
constraints without any experimental data and use the resulting covariance
matrix to transform parameters such that the new parameters are uncorrelated. \todo{Why no Jacobian involved?}

In all but three cases, the Markov chains then give reliable results. But when
we analyze scenarios with $\wilson[NP]{S,P} \ne 0$ and all exp.  constraints,
strong correlations appear again. As a final solution, we then use importance
sampling with the initial proposal function determined by a fit of a Gaussian
mixture to the MCMC samples within the variational Bayes approximation. As the
posterior is unimodal and closely resembles a Gaussian, only a few Gaussian
components are need; i.e., 3 components proved optimal by the variational
approximation to the model evidence. In the most challenging run with 62
parameters, we obtain a relative effective sample size of only 0.038\%. We want
to have enough samples such that the 68\% region is determined with a relative
precision of about 1\%. As a rule of thumb, we consider the ``relative error of
the error'' given by $1/\sqrt{2 N_{\rm eff}}$~\cite[ch. 37]{Agashe:2014kda}.

% consider the binomial model with flat
% prior. Then the standard deviation over the mean of the posterior on the
% binomial parameter $p$ is $\sqrt{ \frac{1-p}{N_{\rm eff} p}}$ where $N_{\rm
%   eff}$ is the number of independent samples.

In the 62D case, we compute $1.1\cdot10^6$ importance samples such that $N_{\rm
  eff} \approx 3500$ and the estimated relative error of the error is 1.2\% and
thus good enough for our purposes.

To create the smooth marginal plots in Figures
\ref{fig:FHvsCT}--\ref{fig:scalar:SM-EFT}, we apply kernel density estimation
for MCMC and importance samples using the fast \texttt{figtree}
library~\cite{morariu08figtree}. In the latter case, we additionally crop 500
outliers.

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
%\section{
%  Standard model predictions
%  \label{app:SM:predictions}
%}
